### 2013-07-11 phd/menger.tex
menger updates

    Let $\mathfrak{C}$ collect all the open covers of $X$. We say $X$ is \scish if there exists a function $f:\mathfrak{C}\times\omega\to\mc{P}(X)$ such that:
      \begin{itemize}
        \item $f(\mc{V},n)$ is $\mc{V}$-compact
        \item $f(\mc{V},n)\subseteq f(\mc{V},n+1)$
        \item $\bigcup_{n<\omega}f(\mc{V},n)=X$
        \item The set
          \[
            g(\mc{U},\mc{V},n) = \bigcup_{m\geq n} f(\mc{U},m)\setminus ( f(\mc{U},m-1)\cup f(\mc{V},m))
          \]
         is $\mc{V}$-compact
      \end{itemize}
  \end{definition}

@@

  \begin{proof}
    Take the injective funcions $f_\alpha$ from Kunen's lemma such that $f_\alpha\rest\beta =^* f_\beta$. Let $\gamma(\mc U)$ identify the least ordinal such that $[\gamma(\mc U),\omega_1)\cup\{\infty\}$ is in a refinement of $\mc U$. Then $f(\mc U,n)=f^{-1}_{\gamma(\mc U)}([0,n]) \cup [\gamma(\mc U),\omega_1)\cup\{\infty\}$ is easily seen to witness the property.
  \end{proof}

@@

  \begin{proof}
    Let $\sigma(\mc{U}_n,\mc{U}_{n+1},n+1)$ cover $f(\mc{U}_{n+1},n+1)$ and $g(\mc{U}_n,\mc{U}_{n+1},n+1)$. If $\mc{U}_0,\mc{U}_1,\dots$ is any play by $C$, then for each $x\in X$, we note that $x\in f(\mc{U}_0,N)$ for some $N$. So either $x\in \bigcap_{m\leq N} f(\mc{U}_m,N)$ and is covered by the strategy during round $N$, or for some $m< N$, $x \in f(\mc{U}_m,N)\setminus (f(\mc{U}_{m},N-1)\cup f(\mc{U}_{m+1},N))$ and is covered by the strategy during round $m+1$.
  \end{proof}

>>>>

    Let $\mathfrak{C}$ collect all the open covers of $X$. We say $X$ is \scish if there exists a function $f:\mathfrak{C}\times\omega\to\mc{P}(X)$ such that:
      \begin{itemize}
        \item $f(\mc{V},n)$ is $\mc{V}$-compact
        \item $f(\mc{V},n)\cap f(\mc{V},n+1) = \emptyset$
        \item $\bigcup_{n<\omega}f(\mc{V},n)=X$
        \item The set
          \[
            g(\mc{U},\mc{V},n+1) = \bigcup_{p\geq n} \Big(f(\mc{U},p+1)\setminus f(\mc{V},p+1)\Big)\setminus \bigcup_{m\leq n}f(\mc{U},m+1)
          \]
         is $\mc{V}$-compact
      \end{itemize}
  \end{definition}

@@

  \begin{proof}
    Take the injective funcions $f_\alpha$ from Kunen's lemma such that $f_\alpha\rest\beta =^* f_\beta$. Let $\gamma(\mc V)$ identify the least ordinal such that $[\gamma(\mc V),\omega_1)\cup\{\infty\}$ is in a refinement of $\mc U$. Then $f$ defined by $f(\mc V,0)=[\gamma(\mc V),\omega_1)\cup\{\infty\}$ and $f(\mc{V},n+1) = f_{\gamma(\mc V)}^{-1}(\{n\})$ is easily seen to witness the property.
  \end{proof}

@@

  \begin{proof}
    Let $\sigma(\mc{U}_0,0)$ cover $f(\mc{U}_0,0)$, and let $\sigma(\mc{U}_n,\mc{U}_{n+1},n+1)$ cover $\bigcup_{m\leq n+1}f(\mc{U}_{n+1},m)$ and $g(\mc{U}_n,\mc{U}_{n+1},n+1)$. If $\mc{U}_0,\mc{U}_1,\dots$ is any play by $C$, then for each $x\in X$, we note that one of the following must occur:
      \begin{itemize}
        \item $x \in f(\mc U_0,0)$ and is covered in the initial round.
        \item $x \in f(\mc U_0,P+1)$ for some $P\geq 0$ and:
        \begin{itemize}
          \item $x\in \bigcup_{m\leq n\leq P} f(\mc{U}_{n+1},m+1)$ and is covered by the strategy by round $P+1$.
          \item $x\in \bigcap_{n\leq P} f(\mc{U}_{n+1},P+1)$ and is covered by the strategy during round $P+1$.
          \item For some $n \leq P$, 
            \[x \in \Big( f(\mc{U}_{n},P+1)\setminus f(\mc{U}_{n+1},P+1) \Big)\setminus \bigcup_{m\leq n} f(\mc{U}_{n+1},m+1) \subseteq g(\mc{U}_m,\mc{U}_{m+1},m+1)\]
           and is covered during round $n+1$.
         \end{itemize}
      \end{itemize}
  \end{proof}
